---
title: "Analysis 2B"
author: "Grace Brown"
date: "2026-02-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggplot2)
library(MuMIn)
library(emmeans)
library(patchwork)
library(broom)

knitr::opts_knit$set(root.dir = "/Users/gracebrown/qp2_2afc")
setwd("/Users/gracebrown/qp2_2afc")

# color-blind-friendly palette
cbPalette <- c("#E69F00", "#CC79A7", "#0072B2", "#D55E00", "#009E73", "#F0E442", "#56B4E9")
cbPalette2 <- c("#E69F00", "#CC79A7", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#56B4E9")
theme_set(theme_bw())
```

## Load Data
```{r load data}
## read messy datasets
### duration of clips
df.time2a <- read_csv("./data/durationlog2a.csv") 
df.time2a <- df.time2a %>% mutate(stimulus = paste0("audio/", filename))
df.time2b <- read_csv("./data/durationlog2b.csv") 
df.time2b <- df.time2b %>% mutate(stimulus = paste0("audio/", filename))
### 2a 
df.trials2a <- read_csv("./data/trials2a.csv") 
df.survey2a <- read_csv("./data/survey2a.csv")
df.trials2a <- left_join(x=df.trials2a,y=df.survey2a,by="subject_id")
df.trials2a <- left_join(x=df.trials2a, y=df.time2a, by="stimulus")
### 2b 
df.trials2b <- read_csv("./data/trials2b.csv")
df.survey2b <- read_csv("./data/survey2b.csv")
df.trials2b <- left_join(x=df.trials2b,y=df.survey2b,by="subject_id")
df.trials2b <- left_join(x=df.trials2b, y=df.time2b, by="stimulus")

## Exclusions by Attention Check
### 2a
df.exclude_attention2a <- df.trials2a %>%  
  filter(trial_type == "html-button-response", correct == FALSE) %>%
  distinct(subject_id)

df.trials2a <- df.trials2a %>% 
  anti_join(df.exclude_attention2a, by = "subject_id")

### 2b 
df.exclude_attention2b <- df.trials2b %>%  
  filter(trial_type == "html-button-response", correct == FALSE) %>%
  distinct(subject_id)

df.trials2b <- df.trials2b %>% 
  anti_join(df.exclude_attention2b, by = "subject_id")

## Exclusions by Trial Completion 
trial_num = 320 # number of listening trials 
### 2a
df.exclude_trial2a <- df.trials2a %>% 
  filter(!is.na(rt), trial_type == "audio-keyboard-response") %>%
  count(subject_id) %>% 
  filter(n / trial_num < 0.85) %>% # subjects with < 85% completion rate excluded
  distinct(subject_id)

df.trials2a <- df.trials2a %>% 
  anti_join(df.exclude_trial2a, by = "subject_id")

### 2b
df.exclude_trial2b <- df.trials2b %>% 
  filter(!is.na(rt), trial_type == "audio-keyboard-response") %>%
  count(subject_id) %>% 
  filter(n / trial_num < 0.85) %>% # subjects with < 85% completion rate excluded
  distinct(subject_id)

df.trials2b <- df.trials2b %>% 
  anti_join(df.exclude_trial2b, by = "subject_id")

## Recode Variables
### 2a
df.trials2a$talker <- factor(df.trials2a$spk, 
                          levels = c(752, 573, 672, 493),
                          labels = c("1F", "2F", "3F", "4F"))
df.trials2a$prev_talker <- factor(df.trials2a$prev_spk, 
                          levels = c(752, 573, 672, 493),
                          labels = c("1F", "2F", "3F", "4F"))
df.trials2a$rt <- as.numeric(df.trials2a$rt)
df.trials2a$log_rt <- log(df.trials2a$rt)
df.trials2a$log_rt[is.infinite(df.trials2a$log_rt)] <- NA
df.trials2a$sentence_id <- as.factor(df.trials2a$sentence_id)
df.trials2a$trial_in_block_recode <- ((df.trials2a$trial_in_block - 1) %% 40) + 1
df.trials2a$block_index <- ((df.trials2a$trial_in_block - 1) %/% 40) + 1
df.trials2a <- df.trials2a %>%
  group_by(subject_id, dimension) %>%
  filter(!is.na(talker)) %>%
  mutate(
    block_rel = ifelse(block_index == min(block_index), "first", "second")
  ) %>%
  ungroup()

### 2b
df.trials2b$talker <- factor(df.trials2b$spk, 
                          levels = c(752, 573, 955, 516),
                          labels = c("1F", "2F", "1M", "2M"))
df.trials2b$prev_talker <- factor(df.trials2b$prev_spk, 
                          levels = c(752, 573, 955, 516),
                          labels = c("1F", "2F", "1M", "2M"))
df.trials2b$rt <- as.numeric(df.trials2b$rt)
df.trials2b$log_rt <- log(df.trials2b$rt)
df.trials2b$log_rt[is.infinite(df.trials2b$log_rt)] <- NA
df.trials2b$sentence_id <- as.factor(df.trials2b$sentence_id)
df.trials2b$trial_in_block_recode <- ((df.trials2b$trial_in_block - 1) %% 40) + 1
df.trials2b$block_index <- ((df.trials2b$trial_in_block - 1) %/% 40) + 1
df.trials2b <- df.trials2b %>%
  group_by(subject_id, dimension) %>%
  filter(!is.na(talker)) %>%
  mutate(
    block_rel = ifelse(block_index == min(block_index), "first", "second")
  ) %>%
  ungroup()

## Join 2a + 2b
df.joint <- rbind(df.trials2a, df.trials2b)
df.joint$study <- factor(df.joint$study_id,
                         levels = c("6973d7039d47152b688034aa", "697ef2a0649c9d3efa7747cf"),
                         labels = c("Same Gender", "Mixed Gender"))
```
## RT Pre-Processing
```{r}
## criteria = filter out trials with RT > mean + 2 sd (across both conditions)
#rt.criteria <- df.joint %>% 
#  filter(trial_type == "audio-keyboard-response") %>%
#  summarise(mean = mean(rt, na.rm = T),
#            sd = sd(rt, na.rm = T))

#rt.cutoff <- rt.criteria$mean + 2 * rt.criteria$sd

#tbl.rt <- df.joint %>% 
#  filter(trial_type == "audio-keyboard-response") %>% 
#  count(rt > 3966)

#df.trials2a <- df.trials2a %>% filter(rt <= rt.cutoff)
#df.trials2b <- df.trials2b %>% filter(rt <= rt.cutoff)
#df.joint <- df.joint %>% filter(rt <= rt.cutoff)

#tbl.rt <- df.joint %>% 
#  filter(trial_type == "audio-keyboard-response") %>% 
#  count(rt > 3966)

df.trials2a  <- df.trials2a  %>%
  group_by(subject_id) %>%
  mutate(
    participant_mean = mean(rt, na.rm = TRUE),
    participant_sd = sd(rt, na.rm = TRUE),
    lower_bound = participant_mean - 2.5 * participant_sd,
    upper_bound = participant_mean + 2.5 * participant_sd
  ) %>%
  filter(rt >= lower_bound & rt <= upper_bound) %>%
  ungroup()

df.trials2b  <- df.trials2b  %>%
  group_by(subject_id) %>%
  mutate(
    participant_mean = mean(rt, na.rm = TRUE),
    participant_sd = sd(rt, na.rm = TRUE),
    lower_bound = participant_mean - 2.5 * participant_sd,
    upper_bound = participant_mean + 2.5 * participant_sd
  ) %>%
  filter(rt >= lower_bound & rt <= upper_bound) %>%
  ungroup()

tbl.rt <- df.joint %>% 
  filter(trial_type == "audio-keyboard-response") %>% 
  count()

df.joint  <- df.joint  %>%
  group_by(subject_id) %>%
  mutate(
    participant_mean = mean(rt, na.rm = TRUE),
    participant_sd = sd(rt, na.rm = TRUE),
    lower_bound = participant_mean - 2.5 * participant_sd,
    upper_bound = participant_mean + 2.5 * participant_sd
  ) %>%
  filter(rt >= lower_bound & rt <= upper_bound) %>%
  ungroup()

tbl.rt2 <- df.joint %>% 
  filter(trial_type == "audio-keyboard-response") %>% 
  count()
```


## Define Response-Specific Datasets
```{r}
## 2B Only Datasets
df.gender2b <- df.trials2b %>%
  filter(label == "masculine" | label == "feminine") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_fem = ifelse(label == "feminine", 1, 0))

df.ease2b <- df.trials2b %>%
  filter(label == "comfortable" | label == "awkward") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_com = ifelse(label == "comfortable", 1, 0))

df.sharp2b <- df.trials2b %>%
  filter(label == "sharp" | label == "dull") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_sharp = ifelse(label == "sharp", 1, 0))

df.express2b <- df.trials2b %>%
  filter(label == "emotive" | label == "robotic") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_emo = ifelse(label == "emotive", 1, 0))

## Joint Datasets
df.gender <- df.joint %>%
  filter(label == "masculine" | label == "feminine") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_fem = ifelse(label == "feminine", 1, 0))

df.ease <- df.joint %>%
  filter(label == "comfortable" | label == "awkward") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_com = ifelse(label == "comfortable", 1, 0))

df.sharp <- df.joint %>%
  filter(label == "sharp" | label == "dull") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_sharp = ifelse(label == "sharp", 1, 0))

df.express <- df.joint %>%
  filter(label == "emotive" | label == "robotic") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_emo = ifelse(label == "emotive", 1, 0))
```

## 2B Visualizations
### tidying up 
```{r}
mean2a <- mean(df.time2a$milliseconddur)
sd2a <- sd(df.time2a$milliseconddur)
mean2b <- mean(df.time2b$milliseconddur)
sd2b <- sd(df.time2b$milliseconddur)

print(c("Mean Duration 2A", mean2a, "Duration St Dev 2A", sd2a))
print(c("Mean Duration 2B", mean2b, "Duration St Dev 2B", sd2b))
```

### feminine / masculine
#### response 
```{r}
plot.gender.resp <- df.gender2b %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_fem,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Feminine'",
       title = "Mean Feminine/Masculine Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2b-plot-gender-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-gender-resp.png",width=7,height=4)

print(plot.gender.resp)
```

#### response time
```{r}
# central tendencies 
plot.gender.rt.mean <- df.gender2b %>% 
  ggplot(mapping = aes(x = talker, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,3000)) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.35) + # dotted line
  labs(x = "Talker",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Feminine/Masculine Response Times by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2b-plot-gender-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-gender-rt-mean.png",width=7,height=4)

print(plot.gender.rt.mean)
  
# trend within block 
plot.gender.rt.trend <- df.gender2b %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  coord_cartesian(ylim = c(1500,2850)) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.35) + # dotted line
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Feminine/Masculine Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-gender-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-gender-rt-trend.png",width=7,height=4)

print(plot.gender.rt.trend)

# trend within block + indiv obs
plot.gender.rt.trend.ind <- df.gender2b %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  #coord_cartesian(ylim = c(1600,2800)) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.5) + # dotted line
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Feminine/Masculine Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-gender-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-gender-rt-trend-ind.png",width=7,height=4)

print(plot.gender.rt.trend.ind)
```

### comfortable / awkward
#### response 
```{r}
plot.ease.resp <- df.ease2b %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_com,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Comfortable'",
       title = "Mean Comfortable/Awkward Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2b-plot-ease-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-ease-resp.png",width=7,height=4)

print(plot.ease.resp)
```

#### response time
```{r}
# central tendencies 
plot.ease.rt.mean <-df.ease2b %>% 
  ggplot(mapping = aes(x = talker, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,3000)) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.35) + # dotted line
  labs(x = "Talker",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Comfortable/Awkward Response Times by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2b-plot-ease-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-ease-rt-mean.png",width=7,height=4)

print(plot.ease.rt.mean)
  
# trend within block 
plot.ease.rt.trend <- df.ease2b %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  coord_cartesian(ylim = c(1500,2850)) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.35) + # dotted line
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Comfortable/Awkward Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-ease-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-ease-rt-trend.png",width=7,height=4)

print(plot.ease.rt.trend)

# trend within block + indiv obs
plot.ease.rt.trend.ind <- df.ease2b %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.5) + # dotted line
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Comfortable/Awkward Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-ease-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-ease-rt-trend-ind.png",width=7,height=4)

print(plot.ease.rt.trend.ind)
```

### sharp / dull
#### response 
```{r}
plot.sharp.resp <- df.sharp2b %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_sharp,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Sharp'",
       title = "Mean Sharp/Dull Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2b-plot-sharp-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-sharp-resp.png",width=7,height=4)

print(plot.sharp.resp)
```

#### response time
```{r}
# central tendencies 
plot.sharp.rt.mean <- df.sharp2b %>% 
  ggplot(mapping = aes(x = talker, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,3000)) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.35) + # dotted line
  labs(x = "Talker",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Sharp/Dull Response Times by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2b-plot-sharp-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-sharp-rt-mean.png",width=7,height=4)

print(plot.sharp.rt.mean)
  
# trend within block 
plot.sharp.rt.trend <- df.sharp2b %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  coord_cartesian(ylim = c(1500,2850)) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.35) + # dotted line
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Sharp/Dull Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-sharp-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-sharp-rt-trend.png",width=7,height=4)

print(plot.sharp.rt.trend)

# trend within block + indiv obs
plot.sharp.rt.trend.ind <- df.sharp2b %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.5) + # dotted line
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Sharp/Dull Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-sharp-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-sharp-rt-trend-ind.png",width=7,height=4)

print(plot.sharp.rt.trend.ind)
```

### emotive / robotic
#### response 
```{r}
plot.express.resp <- df.express2b %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_emo,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Emotive'",
       title = "Mean Emotive/Robotic Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2b-plot-express-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-express-resp.png",width=7,height=4)

print(plot.express.resp)
```

#### response time
```{r}
# central tendencies 
plot.express.rt.mean <- df.express2b %>% 
  ggplot(mapping = aes(x = talker, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,3000)) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.35) + # dotted line
  labs(x = "Talker",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Emotive/Robotic Response Times by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2b-plot-express-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-express-rt-mean.png",width=7,height=4)

print(plot.express.rt.mean)
  
# trend within block 
plot.express.rt.trend <- df.express2b %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  coord_cartesian(ylim = c(1500,2850)) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.35) + # dotted line
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Emotive/Robotic Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-express-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-express-rt-trend.png",width=7,height=4)

print(plot.express.rt.trend)

# trend within block + indiv obs
plot.express.rt.trend.ind <- df.express2b %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  #geom_hline(yintercept = mean2b, linetype = "dotted", alpha = 0.5) + # dotted line
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Emotive/Robotic Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-express-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-express-rt-trend-ind.png",width=7,height=4)

print(plot.express.rt.trend.ind)
```

## 2B Visualizations - Grouped 
### response
```{r}
(plot.gender.resp + plot.ease.resp) /
(plot.sharp.resp + plot.express.resp) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 7),
    axis.title.y = element_text(size = 6),
    axis.text.x  = element_text(size = 7),
    axis.text.y  = element_text(size = 6),
    plot.title   = element_text(size = 9),
    legend.position = "none")

ggsave(file="./analysis/graphs/2b-plot-all-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-all-resp.png",width=7,height=4)
```

### response time
```{r}
(plot.gender.rt.mean + plot.ease.rt.mean) /
(plot.sharp.rt.mean + plot.express.rt.mean) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 7),
    axis.title.y = element_text(size = 4),
    axis.text.x  = element_text(size = 7),
    axis.text.y  = element_text(size = 6),
    plot.title   = element_text(size = 8),
    legend.position = "none")

ggsave(file="./analysis/graphs/2b-plot-all-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-all-rt-mean.png",width=7,height=4)
```

```{r}
(plot.gender.rt.trend + plot.ease.rt.trend) /
(plot.sharp.rt.trend + plot.express.rt.trend) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 7),
    axis.title.y = element_text(size = 4),
    axis.text.x  = element_text(size = 7),
    axis.text.y  = element_text(size = 6),
    plot.title   = element_text(size = 7),
    legend.position = "bottom")

ggsave(file="./analysis/graphs/2b-plot-all-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-all-rt-trend.png",width=7,height=4)
```

## Joint Visualizations
### feminine / masculine
#### response 
```{r}
plot.gender.resp.joint <- df.gender %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = study, 
                       y = response_fem,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker Set",
       y = "Mean Proportion 'Feminine'",
       title = "Mean 1F, 2F Feminine/Masculine Responses by Talker Set") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-gender-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-gender-resp.png",width=7,height=4)

print(plot.gender.resp.joint)

plot.gender.resp.joint.all <- df.gender %>%
  ggplot(mapping = aes(x = study, 
                       y = response_fem,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker Set",
       y = "Mean Proportion 'Feminine'",
       title = "Mean Feminine/Masculine Responses by Talker and Talker Set") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker")
ggsave(file="./analysis/graphs/joint-plot-gender-resp-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-gender-resp-all.png",width=7,height=4)
print(plot.gender.resp.joint.all)

## gender joint best
df.gender.ag <- df.gender %>%
  group_by(study,subject_id,talker) %>% 
  summarise(proportion = mean(response_fem,
                              na.rm = T),
            .groups = 'drop')

plot.gender.resp.best <- df.gender.ag %>%
  ggplot(mapping = aes(x = talker, 
                       y = proportion,
                       fill = talker,
                       color = talker)) +
  geom_point(
    position = position_jitter(width = 0.125, 
                               height = 0.005,
                               seed = 123),
    alpha = 0.2, 
    size = 2
  ) +
  geom_boxplot(
    width = 0.17,
    outlier.shape = NA,
    position = position_nudge(x = 0.25),
    alpha = 0.5,
    notch = F, 
    color = "black"
  ) +
  stat_summary(
    fun.data = "mean_cl_boot",
    geom = "pointrange",
    color = "black",
    size = 0.4,
    position = position_nudge(x = 0.25)
  ) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(~study,
             scales = "free_x")+
  labs(x = "Talker",
       y = "Mean Proportion 'Feminine'",
       title = "Mean Feminine/Masculine Responses by Talker and Talker Set") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/joint-plot-gender-resp-best.pdf",width=6.5,height=5)
ggsave(file="./analysis/graphs/joint-plot-gender-resp-best.png",width=6.5,height=5)

print(plot.gender.resp.best)
```

#### response time
```{r}
# central tendencies 
plot.gender.rt.mean.joint <- df.gender %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = study, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker Set",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean 1F, 2F Feminine/Masculine Response Times by Talker Set") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-gender-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-gender-rt-mean.png",width=7,height=4)

print(plot.gender.rt.mean.joint)

plot.gender.rt.mean.joint.all <- df.gender %>%
  ggplot(mapping = aes(x = study, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker Set",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Feminine/Masculine Response Times by Talker and Talker Set") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-gender-rt-mean-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-gender-rt-mean-all.png",width=7,height=4)

print(plot.gender.rt.mean.joint.all)
  
# trend within block 
plot.gender.rt.trend.joint <- df.gender %>%
  filter(talker == "1F" | talker == "2F") %>%
  filter(block_rel == "first") %>%
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth(alpha = 0.25) + 
  coord_cartesian(ylim = c(1500,2250)) +
  facet_grid(~study) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Feminine/Masculine Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-gender-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-gender-rt-trend.png",width=7,height=4)

# trend within block - all
plot.gender.rt.trend.joint.all <- df.gender %>%
  filter(block_rel == "first") %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth(alpha = 0.25) + 
  coord_cartesian(ylim = c(1500,2250)) +
  facet_grid(~study) + 
  #facet_grid(study~block_rel) + 
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Feminine/Masculine Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-gender-rt-trend-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-gender-rt-trend-all.png",width=7,height=4)

print(plot.gender.rt.trend.joint.all)

# trend within block + indiv obs
plot.gender.rt.trend.ind.joint <- df.gender %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  #geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  coord_cartesian(ylim = c(1500,2250)) +
  facet_grid(~study) + 
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Feminine/Masculine Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-gender-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-gender-rt-trend-ind.png",width=7,height=4)

print(plot.gender.rt.trend.ind.joint)
```

### comfortable / awkward
#### response 
```{r}
plot.ease.resp.joint <- df.ease %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = study, 
                       y = response_com,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker Set",
       y = "Mean Proportion 'Comfortable'",
       title = "Mean 1F, 2F Comfortable/Awkward Responses by Talker Set") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-ease-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-ease-resp.png",width=7,height=4)

print(plot.ease.resp.joint)

plot.ease.resp.joint.all <- df.ease %>%
  ggplot(mapping = aes(x = study, 
                       y = response_com,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker Set",
       y = "Mean Proportion 'Comfortable'",
       title = "Mean Comfortable/Awkward Responses by Talker and Talker Set") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker")
ggsave(file="./analysis/graphs/joint-plot-ease-resp-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-ease-resp-all.png",width=7,height=4)
print(plot.ease.resp.joint.all)

## ease joint best
df.ease.ag <- df.ease %>%
  group_by(study,subject_id,talker) %>% 
  summarise(proportion = mean(response_com,
                              na.rm = T),
            .groups = 'drop')

plot.ease.resp.best <- df.ease.ag %>%
  ggplot(mapping = aes(x = talker, 
                       y = proportion,
                       fill = talker,
                       color = talker)) +
  geom_point(
    position = position_jitter(width = 0.125, 
                               height = 0.005,
                               seed = 123),
    alpha = 0.2, 
    size = 2
  ) +
  geom_boxplot(
    width = 0.17,
    outlier.shape = NA,
    position = position_nudge(x = 0.25),
    alpha = 0.5,
    notch = F, 
    color = "black"
  ) +
  stat_summary(
    fun.data = "mean_cl_boot",
    geom = "pointrange",
    color = "black",
    size = 0.4,
    position = position_nudge(x = 0.25)
  ) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(~study,
             scales = "free_x")+
  labs(x = "Talker",
       y = "Mean Proportion 'Comfortable'",
       title = "Mean Comfortable/Awkward Responses by Study and Talker") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/joint-plot-ease-resp-best.pdf",width=6.5,height=5)
ggsave(file="./analysis/graphs/joint-plot-ease-resp-best.png",width=6.5,height=5)

print(plot.ease.resp.best)
```

#### response time
```{r}
# central tendencies 
plot.ease.rt.mean.joint <- df.ease %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = study, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker Set",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean 1F, 2F Comfortable/Awkward Response Times by Talker Set") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-ease-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-ease-rt-mean.png",width=7,height=4)

print(plot.ease.rt.mean.joint)

plot.ease.rt.mean.joint.all <- df.ease %>%
  ggplot(mapping = aes(x = study, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker Set",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Comfortable/Awkward Response Times by Talker and Talker Set") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-ease-rt-mean-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-ease-rt-mean-all.png",width=7,height=4)

print(plot.ease.rt.mean.joint.all)
  
# trend within block 
plot.ease.rt.trend.joint <- df.ease %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  #coord_cartesian(ylim = c(1600,2800)) +
  facet_grid(~study) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Comfortable/Awkward Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-ease-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-ease-rt-trend.png",width=7,height=4)

print(plot.ease.rt.trend.joint)

# trend within block - all
plot.ease.rt.trend.joint.all <- df.ease %>%
  filter(block_rel == "first") %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth(alpha = 0.25) + 
  coord_cartesian(ylim = c(1500,2850)) +
  facet_grid(~study) +
  #facet_grid(study~block_rel) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Comfortable/Awkward Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-ease-rt-trend-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-ease-rt-trend-all.png",width=7,height=4)

print(plot.ease.rt.trend.joint.all)

# trend within block + indiv obs
plot.ease.rt.trend.ind.joint <- df.ease %>%
  filter(talker == "1F" | talker == "2F") %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  facet_grid(~study) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Comfortable/Awkward Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-ease-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-ease-rt-trend-ind.png",width=7,height=4)

print(plot.ease.rt.trend.ind.joint)
```

### sharp / dull
#### response 
```{r}
plot.sharp.resp.joint <- df.sharp %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = study, 
                       y = response_sharp,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker Set",
       y = "Mean Proportion 'Sharp'",
       title = "Mean 1F, 2F Sharp/Dull Responses by Talker Set") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-sharp-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-sharp-resp.png",width=7,height=4)

print(plot.sharp.resp.joint)

plot.sharp.resp.joint.all <- df.sharp %>%
  ggplot(mapping = aes(x = study, 
                       y = response_sharp,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker Set",
       y = "Mean Proportion 'Sharp'",
       title = "Mean Sharp/Dull Responses by Talker and Talker Set") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-sharp-resp-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-sharp-resp-all.png",width=7,height=4)

print(plot.sharp.resp.joint.all)

## sharp joint best
df.sharp.ag <- df.sharp %>%
  group_by(study,subject_id,talker) %>% 
  summarise(proportion = mean(response_sharp,
                              na.rm = T),
            .groups = 'drop')

plot.sharp.resp.best <- df.sharp.ag %>%
  ggplot(mapping = aes(x = talker, 
                       y = proportion,
                       fill = talker,
                       color = talker)) +
  geom_point(
    position = position_jitter(width = 0.125, 
                               height = 0.005,
                               seed = 123),
    alpha = 0.2, 
    size = 2
  ) +
  geom_boxplot(
    width = 0.17,
    outlier.shape = NA,
    position = position_nudge(x = 0.25),
    alpha = 0.5,
    notch = F, 
    color = "black"
  ) +
  stat_summary(
    fun.data = "mean_cl_boot",
    geom = "pointrange",
    color = "black",
    size = 0.4,
    position = position_nudge(x = 0.25)
  ) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(~study,
             scales = "free_x")+
  labs(x = "Talker",
       y = "Mean Proportion 'Sharp'",
       title = "Mean Sharp/Dull Responses by Study and Talker") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/joint-plot-sharp-resp-best.pdf",width=6.5,height=5)
ggsave(file="./analysis/graphs/joint-plot-sharp-resp-best.png",width=6.5,height=5)

print(plot.sharp.resp.best)
```

#### response time
```{r}
# central tendencies 
plot.sharp.rt.mean.joint <- df.sharp %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = study, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker Set",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean 1F, 2F Sharp/Dull Response Times by Talker Set") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-sharp-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-sharp-rt-mean.png",width=7,height=4)

print(plot.sharp.rt.mean.joint)

plot.sharp.rt.mean.joint.all <- df.sharp %>%
  ggplot(mapping = aes(x = study, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker Set",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Sharp/Dull Response Times by Talker and Talker Set") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-sharp-rt-mean-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-sharp-rt-mean-all.png",width=7,height=4)

print(plot.sharp.rt.mean.joint.all)
  
# trend within block 
plot.sharp.rt.trend.joint <- df.sharp %>%
  filter(talker == "1F" | talker == "2F") %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  #coord_cartesian(ylim = c(1600,2800)) +
  facet_grid(~study) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Sharp/Dull Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-sharp-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-sharp-rt-trend.png",width=7,height=4)

print(plot.sharp.rt.trend.joint)

# trend within block - all
plot.sharp.rt.trend.joint.all <- df.sharp %>%
  filter(block_rel == "first") %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth(alpha = 0.25) + 
  coord_cartesian(ylim = c(1500,2850)) +
  facet_grid(~study) +
  #facet_grid(study~block_rel) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Sharp/Dull Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-sharp-rt-trend-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-sharp-rt-trend-all.png",width=7,height=4)

print(plot.sharp.rt.trend.joint.all)

# trend within block + indiv obs
plot.sharp.rt.trend.ind.joint <- df.sharp %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  facet_grid(~study) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Sharp/Dull Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-sharp-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-sharp-rt-trend-ind.png",width=7,height=4)

print(plot.sharp.rt.trend.ind.joint)
```

### emotive / robotic
#### response 
```{r}
plot.express.resp.joint <- df.express %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = study, 
                       y = response_emo,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker Set",
       y = "Mean Proportion 'Emotive'",
       title = "Mean 1F, 2F Emotive/Robotic Responses by Talker Set") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-express-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-express-resp.png",width=7,height=4)

print(plot.express.resp.joint)

plot.express.resp.joint.all <- df.express %>%
  ggplot(mapping = aes(x = study, 
                       y = response_emo,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker Set",
       y = "Mean Proportion 'Emotive'",
       title = "Mean Emotive/Robotic Responses by Talker and Talker Set") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-express-resp-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-express-resp-all.png",width=7,height=4)

print(plot.express.resp.joint.all)

## express joint best
df.express.ag <- df.express %>%
  group_by(study,subject_id,talker) %>% 
  summarise(proportion = mean(response_emo,
                              na.rm = T),
            .groups = 'drop')

plot.express.resp.best <- df.express.ag %>%
  ggplot(mapping = aes(x = talker, 
                       y = proportion,
                       fill = talker,
                       color = talker)) +
  geom_point(
    position = position_jitter(width = 0.125, 
                               height = 0.005,
                               seed = 123),
    alpha = 0.2, 
    size = 2
  ) +
  geom_boxplot(
    width = 0.17,
    outlier.shape = NA,
    position = position_nudge(x = 0.25),
    alpha = 0.5,
    notch = F, 
    color = "black"
  ) +
  stat_summary(
    fun.data = "mean_cl_boot",
    geom = "pointrange",
    color = "black",
    size = 0.4,
    position = position_nudge(x = 0.25)
  ) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(~study,
             scales = "free_x")+
  labs(x = "Talker",
       y = "Mean Proportion 'Emotive'",
       title = "Mean Emotive/Robotic Responses by Study and Talker") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/joint-plot-express-resp-best.pdf",width=6.5,height=5)
ggsave(file="./analysis/graphs/joint-plot-express-resp-best.png",width=6.5,height=5)

print(plot.express.resp.best)
```

#### response time
```{r}
# central tendencies 
plot.express.rt.mean.joint <- df.express %>%
  filter(talker == "1F" | talker == "2F") %>% 
  ggplot(mapping = aes(x = study, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker Set",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean 1F, 2F Emotive/Robotic Response Times by Talker Set") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-express-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-express-rt-mean.png",width=7,height=4)

print(plot.express.rt.mean.joint)

plot.express.rt.mean.joint.all <- df.express %>%
  ggplot(mapping = aes(x = study, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar",
               position = position_dodge(width = .9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(width = .9)) + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker Set",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Emotive/Robotic Response Times by Talker and Talker Set") + 
  scale_fill_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-express-rt-mean-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-express-rt-mean-all.png",width=7,height=4)

print(plot.express.rt.mean.joint.all)
  
# trend within block 
plot.express.rt.trend.joint <- df.express %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  #coord_cartesian(ylim = c(1600,2800)) +
  facet_grid(~study) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Emotive/Robotic Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-express-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-express-rt-trend.png",width=7,height=4)

print(plot.express.rt.trend.joint)

# trend within block - all
plot.express.rt.trend.joint.all <- df.express %>%
  filter(block_rel == "first") %>%
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth(alpha = 0.25) + 
  coord_cartesian(ylim = c(1500,2850)) +
  facet_grid(~study) +
  #facet_grid(study~block_rel) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Emotive/Robotic Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-express-rt-trend-all.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-express-rt-trend-all.png",width=7,height=4)

print(plot.express.rt.trend.joint.all)

# trend within block + indiv obs
plot.express.rt.trend.ind.joint <- df.express %>%
  filter(talker == "1F" | talker == "2F") %>%
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  facet_grid(~study) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Emotive/Robotic Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-express-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-express-rt-trend-ind.png",width=7,height=4)

print(plot.express.rt.trend.ind.joint)
```

## Joint Visualizations - Grouped
### response - 1F and 2F 
```{r}
(plot.gender.resp.joint + plot.ease.resp.joint) /
(plot.sharp.resp.joint + plot.express.resp.joint) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 6),
    axis.text.x  = element_text(size = 6),
    axis.text.y  = element_text(size = 5),
    plot.title   = element_text(size = 8),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6),
    legend.position = "bottom")

ggsave(file="./analysis/graphs/joint-plot-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-resp.png",width=7,height=4)
```

### response - all talkers
```{r}
(plot.gender.resp.joint.all + plot.ease.resp.joint.all) /
(plot.sharp.resp.joint.all + plot.express.resp.joint.all) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 6),
    axis.text.x  = element_text(size = 6),
    axis.text.y  = element_text(size = 5),
    plot.title   = element_text(size = 7),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6),
    legend.position = "bottom")

ggsave(file="./analysis/graphs/joint-plot-all-resp.pdf",width=8,height=4)
ggsave(file="./analysis/graphs/joint-plot-all-resp.png",width=8,height=4)
```

```{r}
plot.gender.resp.best <- plot.gender.resp.best + labs(title = NULL)
plot.ease.resp.best <- plot.ease.resp.best + labs(title = NULL)
plot.sharp.resp.best <- plot.sharp.resp.best + labs(title = NULL)
plot.express.resp.best <- plot.express.resp.best + labs(title = NULL)

(plot.gender.resp.best + plot.ease.resp.best) /
(plot.sharp.resp.best + plot.express.resp.best) +
  plot_annotation(
    "Mean Responses by Response Pair, Talker, and Talker Set",
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 9),
    axis.title.y = element_text(size = 9),
    axis.text.x  = element_text(size = 7),
    axis.text.y  = element_text(size = 7),
    plot.title   = element_text(size = 14),
    legend.position = "none")

ggsave(file="./analysis/graphs/joint-plot-all-resp-best.pdf",width=12,height=6)
ggsave(file="./analysis/graphs/joint-plot-all-resp-best.png",width=12,height=6)
```

### response time - 1F and 2F
```{r}
(plot.gender.rt.mean.joint + plot.ease.rt.mean.joint) /
(plot.sharp.rt.mean.joint + plot.express.rt.mean.joint) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 4),
    axis.text.x  = element_text(size = 6),
    axis.text.y  = element_text(size = 5),
    plot.title   = element_text(size = 7),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6),
    legend.position = "bottom")

ggsave(file="./analysis/graphs/joint-plot-rt-mean.pdf",width=7,height=5)
ggsave(file="./analysis/graphs/joint-plot-rt-mean.png",width=7,height=5)
```

### response time - all talkers
```{r}
(plot.gender.rt.mean.joint.all + plot.ease.rt.mean.joint.all) /
(plot.sharp.rt.mean.joint.all + plot.express.rt.mean.joint.all) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 4),
    axis.text.x  = element_text(size = 6),
    axis.text.y  = element_text(size = 5),
    plot.title   = element_text(size = 7),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6),
    legend.position = "bottom")

ggsave(file="./analysis/graphs/joint-plot-all-rt-mean.pdf",width=7,height=5)
ggsave(file="./analysis/graphs/joint-plot-all-rt-mean.png",width=7,height=5)
```

### response time - all talkers
```{r}
plot.gender.rt.trend.joint.all <- plot.gender.rt.trend.joint.all + labs(title = NULL)
plot.ease.rt.trend.joint.all <- plot.ease.rt.trend.joint.all + labs(title = NULL)
plot.sharp.rt.trend.joint.all <- plot.sharp.rt.trend.joint.all + labs(title = NULL)
plot.express.rt.trend.joint.all <- plot.express.rt.trend.joint.all + labs(title = NULL)

(plot.gender.rt.trend.joint.all + plot.ease.rt.trend.joint.all) /
(plot.sharp.rt.trend.joint.all + plot.express.rt.trend.joint.all) +
  plot_annotation("Mean Response Times by Trial, Talker, and Talker Set", 
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14),
      plot.title = element_text(size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 4),
    axis.text.x  = element_text(size = 6),
    axis.text.y  = element_text(size = 5),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6),
    strip.text = element_text(size = 6),
    legend.position = "bottom") 

ggsave(file="./analysis/graphs/joint-plot-all-rt-trend.pdf",width=7,height=5)
ggsave(file="./analysis/graphs/joint-plot-all-rt-trend.png",width=7,height=5)
```

## 2B Models
### feminine / masculine
```{r}
fit.gender2b <- glmer(formula = response_fem ~ 1 + talker + 
                      scale(trial_in_block_recode) +
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = df.gender2b)

summary(fit.gender2b)

emmeans(fit.gender2b, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.gender.rt2b <- lmer(formula = rt ~ 1 + talker*scale(trial_in_block_recode) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.gender2b)

summary(fit.gender.rt2b)

emmeans(fit.gender.rt2b, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.gender.logrt2b <- lmer(formula = log_rt ~ 1 + talker*scale(trial_in_block_recode) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.gender2b)

summary(fit.gender.logrt2b)

emmeans(fit.gender.logrt2b, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()
```

### comfortable / awkward
```{r}
fit.ease2b <- glmer(formula = response_com ~ 1 + talker +
                    scale(trial_in_block_recode) +
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = df.ease2b)

summary(fit.ease2b)

emmeans(fit.ease2b, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.ease.rt2b <- lmer(formula = rt ~ 1 + talker*scale(trial_in_block_recode) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.ease2b)

summary(fit.ease.rt2b)

emmeans(fit.ease.rt2b, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

fit.ease.logrt2b <- lmer(formula = log_rt ~ 1 + talker*scale(trial_in_block_recode) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.ease2b)

summary(fit.ease.logrt2b)

emmeans(fit.ease.logrt2b, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()
```

### sharp / dull
```{r}
fit.sharp2b <- glmer(formula = response_sharp ~ 1 + talker +
                       scale(trial_in_block_recode) +
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = df.sharp2b)

summary(fit.sharp2b)

emmeans(fit.sharp2b, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.sharp.rt2b <- lmer(formula = rt ~ 1 + talker*scale(trial_in_block_recode) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.sharp2b)

summary(fit.sharp.rt2b)

emmeans(fit.sharp.rt2b, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

fit.sharp.logrt2b <- lmer(formula = log_rt ~ 1 + talker*scale(trial_in_block_recode) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.sharp2b)

summary(fit.sharp.logrt2b)

emmeans(fit.sharp.logrt2b, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()
```

### emotive / robotic
```{r}
fit.express2b <- glmer(formula = response_emo ~ 1 + talker +
                       scale(trial_in_block_recode) +
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = df.express2b)

summary(fit.express2b)

emmeans(fit.express2b, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.express.rt2b <- lmer(formula = rt ~ 1 + talker*scale(trial_in_block_recode) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.express2b)

summary(fit.express.rt2b)

emmeans(fit.express.rt2b, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

fit.express.logrt2b <- lmer(formula = log_rt ~ 1 + talker*scale(trial_in_block_recode) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.express2b)

summary(fit.express.logrt2b)

emmeans(fit.express.logrt2b, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()
```

### response times over all response item pairs
```{r}
fit.all.rt2b <- lmer(formula = rt ~ 1 + talker*dimension*scale(trial_in_block_recode) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.trials2b)

summary(fit.all.rt2b)

emmeans(fit.all.rt2b, 
        specs = pairwise ~ dimension,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.all.rt2b, 
        specs = pairwise ~ talker | dimension,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()

fit.all.logrt2b <- lmer(formula = log_rt ~ 1 + talker*dimension*scale(trial_in_block_recode) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.trials2b)

summary(fit.all.logrt2b)

emmeans(fit.all.logrt2b, 
        specs = pairwise ~ dimension,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.all.logrt2b, 
        specs = pairwise ~ talker | dimension,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()
```

## Joint Models
### feminine / masculine
```{r}
fit.gender <- glmer(formula = response_fem ~ 1 + talker*study + 
                      scale(trial_in_block_recode) + 
                      scale(milliseconddur) +
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = filter(df.gender, 
                                 talker == "1F" | talker == "2F"))

summary(fit.gender)

emmeans(fit.gender, 
        specs = pairwise ~ talker | study) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.gender, 
        specs = pairwise ~ study | talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.gender.rt <- lmer(formula = rt ~ 1 + talker*study*scale(trial_in_block_recode) +
                        scale(milliseconddur) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = filter(df.gender,
                                 talker == "1F" | talker == "2F"))

summary(fit.gender.rt)

emmeans(fit.gender.rt, 
        specs = pairwise ~ talker | study) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.gender.rt, 
        specs = pairwise ~ study | talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.gender.logrt <- lmer(formula = log_rt ~ 1 + talker*study*scale(trial_in_block_recode) +
                           scale(milliseconddur) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = filter(df.gender,
                                 talker == "1F" | talker == "2F"))

summary(fit.gender.logrt)

emmeans(fit.gender.logrt, 
        specs = pairwise ~ talker | study) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.gender.logrt, 
        specs = pairwise ~ study | talker) %>% 
  pluck("contrasts") %>%
  summary()
```

### comfortable / awkward
```{r}
fit.ease <- glmer(formula = response_com ~ 1 + talker*study +
                    scale(trial_in_block_recode) +
                    scale(milliseconddur) +
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = filter(df.ease,
                                 talker == "1F" | talker == "2F"))

summary(fit.ease)

emmeans(fit.ease, 
        specs = pairwise ~ talker | study) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.ease, 
        specs = pairwise ~ study | talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.ease.rt <- lmer(formula = rt ~ 1 + talker*study*scale(trial_in_block_recode) +
                      scale(milliseconddur) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = filter(df.ease,
                                 talker == "1F" | talker == "2F"))

summary(fit.ease.rt)

emmeans(fit.ease.rt, 
        specs = pairwise ~ talker | study,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.ease.rt, 
        specs = pairwise ~ study | talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

fit.ease.logrt <- lmer(formula = log_rt ~ 1 + talker*study*scale(trial_in_block_recode) +
                           scale(milliseconddur) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = filter(df.ease,
                                 talker == "1F" | talker == "2F"))

summary(fit.ease.logrt)

emmeans(fit.ease.logrt, 
        specs = pairwise ~ talker | study) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.ease.logrt, 
        specs = pairwise ~ study | talker) %>% 
  pluck("contrasts") %>%
  summary()
```

### sharp / dull
```{r}
fit.sharp <- glmer(formula = response_sharp ~ 1 + talker*study +
                       scale(trial_in_block_recode) +
                     scale(milliseconddur) +
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = filter(df.sharp,
                                 talker == "1F" | talker == "2F"))

summary(fit.sharp)

emmeans(fit.sharp, 
        specs = pairwise ~ talker | study) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.sharp, 
        specs = pairwise ~ study | talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.sharp.rt <- lmer(formula = rt ~ 1 + talker*study*scale(trial_in_block_recode) +
                       scale(milliseconddur) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = filter(df.sharp,
                                 talker == "1F" | talker == "2F"))

summary(fit.sharp.rt)

emmeans(fit.sharp.rt, 
        specs = pairwise ~ talker | study,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.sharp.rt, 
        specs = pairwise ~ study | talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

fit.sharp.logrt <- lmer(formula = log_rt ~ 1 + talker*study*scale(trial_in_block_recode) +
                       scale(milliseconddur) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = filter(df.sharp,
                                 talker == "1F" | talker == "2F"))

summary(fit.sharp.logrt)

emmeans(fit.sharp.logrt, 
        specs = pairwise ~ talker | study,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.sharp.logrt, 
        specs = pairwise ~ study | talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()
```

### emotive / robotic
```{r}
fit.express <- glmer(formula = response_emo ~ 1 + talker*study +
                       scale(trial_in_block_recode) +
                       scale(milliseconddur) +
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = filter(df.express,
                                 talker == "1F" | talker == "2F"))

summary(fit.express)

emmeans(fit.express, 
        specs = pairwise ~ talker | study) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.express, 
        specs = pairwise ~ study | talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

fit.express.rt <- lmer(formula = rt ~ 1 + talker*study*scale(trial_in_block_recode) +
                         scale(milliseconddur) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = filter(df.express,
                                 talker == "1F" | talker == "2F"))

summary(fit.express.rt)

emmeans(fit.express.rt, 
        specs = pairwise ~ talker | study,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.express.rt, 
        specs = pairwise ~ study | talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

fit.express.logrt <- lmer(formula = log_rt ~ 1 + talker*study*scale(trial_in_block_recode) +
                         scale(milliseconddur) +
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = filter(df.express,
                                 talker == "1F" | talker == "2F"))

summary(fit.express.logrt)

emmeans(fit.express.logrt, 
        specs = pairwise ~ talker | study,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.express.logrt, 
        specs = pairwise ~ study | talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()
```

### response times over all response item pairs
```{r}
fit.all.rt <- lmer(formula = rt ~ 1 + talker*dimension*study*scale(trial_in_block_recode) +
                     scale(milliseconddur) +
                         (1 | subject_id) +
                       (1 | sentence_id), #+
                       #(1 | block_index),
                   data = filter(df.joint,
                                 talker == "1F" | talker == "2F"))

summary(fit.all.rt)

emmeans(fit.all.rt, 
        specs = pairwise ~ study | dimension*talker,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.all.rt, 
        specs = pairwise ~ talker | dimension*study,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()

## log rt

fit.all.logrt <- lmer(formula = log_rt ~ 1 + talker*dimension*study*scale(trial_in_block_recode) +
                     scale(milliseconddur) +
                         (1 | subject_id) +
                       (1 | sentence_id), #+
                       #(1 | block_index),
                   data = filter(df.joint,
                                 talker == "1F" | talker == "2F"))

summary(fit.all.logrt)

emmeans(fit.all.logrt, 
        specs = pairwise ~ study | dimension*talker,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.all.logrt, 
        specs = pairwise ~ talker | dimension*study,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()
```

## Exploratory Analysis - 2B
### tidying up 
```{r}
prev_talker.labs <- c("Prev: 1F", "Prev: 2F", "Prev: 1M", "Prev: 2M")
names(prev_talker.labs) <- c("1F", "2F", "1M", "2M")
```

### feminine / masculine
#### response by prev_talker
```{r}
plot.gender.resp.expl <- df.gender2b %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_fem,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Feminine'",
       title = "Mean Feminine/Masculine Responses by Talker") + 
  facet_grid(~prev_talker,
             labeller = labeller(prev_talker = prev_talker.labs)) +
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-gender-resp-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-gender-resp-expl.png",width=7,height=4)

print(plot.gender.resp.expl)
```

#### response by trial
```{r}
# trend within block + indiv obs
plot.gender.trial.expl <- df.gender %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = response_fem, 
                       group = talker,
                       color = talker)) + 
  geom_smooth(se = T) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(study~block_rel) +
  labs(x = "Within-Block Trial #",
       y = "Mean Proportion 'Feminine'",
       title = "Mean Feminine/Masculine Responses by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-gender-trial-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-gender-trial-expl.png",width=7,height=4)

print(plot.gender.trial.expl)
```


### comfortable / awkward
#### response by prev_talker
```{r}
plot.ease.resp.expl <- df.ease2b %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_com,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Comfortable'",
       title = "Mean Comfortable/Awkward Responses by Talker") + 
  facet_grid(~prev_talker,
             labeller = labeller(prev_talker = prev_talker.labs)) +
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-ease-resp-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-ease-resp-expl.png",width=7,height=4)

print(plot.ease.resp.expl)
```

#### response by trial
```{r}
# trend within block + indiv obs
plot.ease.trial.expl <- df.ease %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = response_com, 
                       group = talker,
                       color = talker)) + 
  geom_smooth(se = T) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(study~block_rel) +
  labs(x = "Within-Block Trial #",
       y = "Mean Proportion 'Comfortable'",
       title = "Mean Comfortable/Awkward Responses by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-ease-trial-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-ease-trial-expl.png",width=7,height=4)

print(plot.ease.trial.expl)
```

### sharp / dull
#### response by prev_talker
```{r}
plot.sharp.resp.expl <- df.sharp2b %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_sharp,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Sharp'",
       title = "Mean Sharp/Dull Responses by Talker") + 
  facet_grid(~prev_talker,
             labeller = labeller(prev_talker = prev_talker.labs)) +
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-sharp-resp-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-sharp-resp-expl.png",width=7,height=4)

print(plot.sharp.resp.expl)
```

#### response by trial
```{r}
# trend within block + indiv obs
plot.sharp.trial.expl <- df.sharp %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = response_sharp, 
                       group = talker,
                       color = talker)) + 
  geom_smooth(se = T) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(study~block_rel) +
  labs(x = "Within-Block Trial #",
       y = "Mean Proportion 'Sharp'",
       title = "Mean Sharp/Dull Responses by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-sharp-trial-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-sharp-trial-expl.png",width=7,height=4)

print(plot.sharp.trial.expl)
```

### emotive / robotic
#### response by prev_talker
```{r}
plot.express.resp.expl <- df.express2b %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_emo,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Emotive'",
       title = "Mean Emotive/Robotic Responses by Talker") + 
  facet_grid(~prev_talker,
             labeller = labeller(prev_talker = prev_talker.labs)) +
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2b-plot-express-resp-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2b-plot-express-resp-expl.png",width=7,height=4)

print(plot.express.resp.expl)
```

#### response by trial
```{r}
# trend within block + indiv obs
plot.express.trial.expl <- df.express %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = response_emo, 
                       group = talker,
                       color = talker)) + 
  geom_smooth(se = T) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(study~block_rel) +
  labs(x = "Within-Block Trial #",
       y = "Mean Proportion 'Emotive'",
       title = "Mean Emotive/Robotic Responses by Talker and Trial") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

ggsave(file="./analysis/graphs/joint-plot-express-trial-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/joint-plot-express-trial-expl.png",width=7,height=4)

print(plot.express.trial.expl)
```

### extremity stuff
```{r}
# Calculate extremity (distance from chance)
df.extremes.gender <- df.gender %>%
  group_by(study, subject_id, talker) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    proportion = mean(response_fem), # assuming binary 0/1
    extremity = abs(proportion - 0.5),
    .groups = "drop"
  )

df.extremes.ease <- df.ease %>%
  group_by(study, subject_id, talker) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    proportion = mean(response_com), # assuming binary 0/1
    extremity = abs(proportion - 0.5),
    .groups = "drop"
  )

df.extremes.sharp <- df.sharp %>%
  group_by(study, subject_id, talker) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    proportion = mean(response_sharp), # assuming binary 0/1
    extremity = abs(proportion - 0.5),
    .groups = "drop"
  )

df.extremes.express <- df.express %>%
  group_by(study, subject_id, talker) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    proportion = mean(response_emo), # assuming binary 0/1
    extremity = abs(proportion - 0.5),
    .groups = "drop"
  )

# Correlations by response pair
correlations.gender <- df.extremes.gender %>%
  group_by(study) %>%
  summarise(
    r = cor(extremity, mean_rt, use = "complete.obs"),
    p = cor.test(extremity, mean_rt)$p.value,
    n = n()
  )

correlations.ease <- df.extremes.ease %>%
  group_by(study) %>%
  summarise(
    r = cor(extremity, mean_rt, use = "complete.obs"),
    p = cor.test(extremity, mean_rt)$p.value,
    n = n()
  )

correlations.sharp <- df.extremes.sharp %>%
  group_by(study) %>%
  summarise(
    r = cor(extremity, mean_rt, use = "complete.obs"),
    p = cor.test(extremity, mean_rt)$p.value,
    n = n()
  )

correlations.express <- df.extremes.express %>%
  group_by(study) %>%
  summarise(
    r = cor(extremity, mean_rt, use = "complete.obs"),
    p = cor.test(extremity, mean_rt)$p.value,
    n = n()
  )

print(correlations.gender)
print(correlations.ease)
print(correlations.sharp)
print(correlations.express)
```

```{r}
plot.gender.extreme <- ggplot(data = filter(df.extremes.gender,
                                             talker == "1F" | talker == "2F"), 
                              mapping = aes(x = extremity, 
                                            y = mean_rt, 
                                            color = talker)) +
  geom_point(alpha = 0.5,
             position = position_jitter(width = 0.01)) + 
  geom_smooth(method = "lm", 
              color = "black") + 
  facet_grid(~study) + 
  coord_cartesian(ylim = c(300, 3500)) + 
  labs(x = "Extremity (Distance from Average At-Chance 'Feminine' Response)",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Response Times Predicted by Extremity") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

plot.ease.extreme <- ggplot(data = filter(df.extremes.ease,
                                             talker == "1F" | talker == "2F"), 
                              mapping = aes(x = extremity, 
                                            y = mean_rt, 
                                            color = talker)) +
  geom_point(alpha = 0.5,
             position = position_jitter(width = 0.01)) + 
  geom_smooth(method = "lm", 
              color = "black") + 
  facet_grid(~study) + 
  coord_cartesian(ylim = c(300, 3500)) +
  labs(x = "Extremity (Distance from Average At-Chance 'Comfortable' Response)",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Response Times Predicted by Extremity") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

plot.sharp.extreme <- ggplot(data = filter(df.extremes.sharp,
                                             talker == "1F" | talker == "2F"), 
                              mapping = aes(x = extremity, 
                                            y = mean_rt, 
                                            color = talker)) +
  geom_point(alpha = 0.5,
             position = position_jitter(width = 0.01)) + 
  geom_smooth(method = "lm", 
              color = "black") + 
  facet_grid(~study) + 
  coord_cartesian(ylim = c(300, 3500)) +
  labs(x = "Extremity (Distance from Average At-Chance 'Sharp' Response)",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Response Times Predicted by Extremity") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")

plot.express.extreme <- ggplot(data = filter(df.extremes.express,
                                             talker == "1F" | talker == "2F"),
                              mapping = aes(x = extremity, 
                                            y = mean_rt, 
                                            color = talker)) +
  geom_point(alpha = 0.5,
             position = position_jitter(width = 0.01)) + 
  geom_smooth(method = "lm", 
              color = "black") + 
  facet_grid(~study) + 
  coord_cartesian(ylim = c(300, 3500)) +
  labs(x = "Extremity (Distance from Average At-Chance 'Emotive' Response)",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Response Times Predicted by Extremity") + 
  scale_color_manual(values = cbPalette2,
                    name = "Talker")
  
```


```{r}
(plot.gender.extreme + plot.ease.extreme) /
(plot.sharp.extreme + plot.express.extreme) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 4),
    axis.text.x  = element_text(size = 6),
    axis.text.y  = element_text(size = 5),
    plot.title   = element_text(size = 0),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6),
    strip.text = element_text(size = 6),
    legend.position = "bottom")

ggsave(file="./analysis/graphs/joint-plot-extreme.pdf",width=9,height=5)
ggsave(file="./analysis/graphs/joint-plot-extreme.png",width=9,height=5)
```

### response variability over trials 
```{r}
# Step 1: Identify first and last quartile of trials within each block
df.gender.position <- df.gender %>%
  group_by(subject_id, talker, study, block_rel) %>%
  arrange(trial_in_block_recode) %>%  # Make sure trials are in order
  mutate(
    trial_number_in_block = row_number(),
    total_trials_in_block = n(),
    # Determine if trial is in first or last quartile
    position = case_when(
      trial_number_in_block <= ceiling(total_trials_in_block * 0.25) ~ "first_quart",
      trial_number_in_block > floor(total_trials_in_block * 0.75) ~ "last_quart",
      TRUE ~ "middle"
    )
  ) %>%
  ungroup() %>%
  # Keep only first and last quartile
  filter(position %in% c("first_quart", "last_quart"))

df.gender.part.var <- df.gender.position %>%
  group_by(subject_id, talker, study, block_rel, position) %>%
  summarise(
    mean_within = mean(response_fem),
    sd_within = sd(response_fem),
    cv_within = (sd(response_fem, na.rm = TRUE) / mean(response_fem, na.rm = TRUE)) * 100,
    .groups = 'drop'
  ) 
df.gender.part.ag <- df.gender.part.var %>%
  group_by(talker, study, position) %>%
  summarise(
    mean_mean_within = mean(mean_within, na.rm = TRUE),
    mean_within_sd = mean(sd_within, na.rm = TRUE),
    .groups = 'drop'
  )

# Step 2: Calculate mean proportion for each participant-talker-study-response_type-quartile combination
df.gender.pos.ag <- df.gender.position %>%
  group_by(subject_id, talker, study, block_rel, position) %>%
  summarise(
    proportion = mean(response_fem, na.rm = TRUE),
    .groups = 'drop'
  )

# Step 3: Calculate variability (SD or variance) for each talker-study-response_type-quartile combination
df.gender.var <- df.gender.pos.ag %>%
  group_by(talker, study, block_rel, position) %>%
  summarise(
    mean_proportion = mean(proportion, na.rm = TRUE),
    sd_proportion = sd(proportion, na.rm = TRUE),
    variance = var(proportion, na.rm = TRUE),
    n_participants = n(),
    se = sd_proportion / sqrt(n_participants),
    .groups = 'drop'
  )

# Step 6: Visualize variability - Option 3: Violin plots with points
library(ggdist)

df.gender.pos.ag %>% 
  ggplot(aes(x = position, y = proportion, fill = position)) +
  stat_halfeye(
    adjust = 1,
    width = 0.6,
    .width = 0,
    justification = -0.2,
    point_colour = NA
  ) +
  geom_boxplot(
    width = 0.12,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  geom_point(
    position = position_jitter(width = 0.05, height = 0, seed = 123),
    alpha = 0.3,
    size = 1
  ) +
  facet_grid(study ~ talker) +
  labs(
    x = "Block Position",
    y = "Proportion",
    title = "Response Variability: First vs Last Quartile"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.text = element_text(size = 8)
  )

# Step 7: Visualize variability - Option 4: Line plot showing change in variability
ggplot(df.gender.var, 
       aes(x = position, y = sd_proportion, 
           color = talker, group = talker)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  facet_grid(study ~ block_rel) +
  labs(
    x = "Block Position",
    y = "Standard Deviation",
    color = "Talker",
    title = "Change in Variability from First to Last Quartile"
  ) +
  theme_minimal()

```


```{r}
# Step 1: Calculate within-participant variability
df.gender.position <- df.gender %>%
  group_by(subject_id, talker, study, block_rel) %>%
  arrange(trial_in_block_recode) %>%  # Make sure trials are in order
  mutate(
    trial_number_in_block = row_number(),
    total_trials_in_block = n(),
    # Determine if trial is in first or last quartile
    position = case_when(
      trial_number_in_block <= ceiling(total_trials_in_block * 0.25) ~ "first_quart",
      trial_number_in_block > floor(total_trials_in_block * 0.75) ~ "last_quart",
      TRUE ~ "middle"
    )
  ) %>%
  ungroup() %>%
  # Keep only first and last quartile
  filter(position %in% c("first_quart", "last_quart"))

df.gender.part.var <- df.gender.position %>%
  group_by(subject_id, talker, study, block_rel, position) %>%
  summarise(
    mean_response = mean(response_fem),
    sd_response = sd(response_fem),
    .groups = 'drop'
  ) 

# Step 2: Calculate group-level means and SDs
df.gender.part.sum <- df.gender.part.var %>%
  group_by(talker, study, position) %>%
  summarise(
    mean_of_means = mean(mean_response, na.rm = TRUE),
    mean_of_sds = mean(sd_response, na.rm = TRUE),
    se_of_means = sd(mean_response, na.rm = TRUE) / sqrt(n()),
    se_of_sds = sd(sd_response, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

plot.gender.mean.expl <- ggplot(df.gender.part.sum, 
                 aes(x = talker, y = mean_of_means, fill = position)) +
  geom_col(position = position_dodge(width = 0.8), alpha = 0.7) +
  facet_grid(~study,
             scales = "free_x") +
  labs(x = "Talker", y = "Mean Response", fill = "Quartile") +
  theme_minimal()

plot.gender.sd.expl <- ggplot(df.gender.part.sum, 
               aes(x = talker, y = mean_of_sds, fill = position)) +
  geom_col(position = position_dodge(width = 0.8), alpha = 0.7) +
  facet_grid(~study,
             scales = "free_x") +
  coord_cartesian(ylim = c(0,0.35)) +
  labs(x = "Talker", 
       y = "Response Variability (SD)", 
       fill = "Quartile", 
       title = "Feminine/Masculine Trials") 

plot.gender.mean.expl / plot.gender.sd.expl + plot_layout(guides = "collect")
```

```{r}
# Step 1: Calculate within-participant variability
df.ease.position <- df.ease %>%
  group_by(subject_id, talker, study, block_rel) %>%
  arrange(trial_in_block_recode) %>%  # Make sure trials are in order
  mutate(
    trial_number_in_block = row_number(),
    total_trials_in_block = n(),
    # Determine if trial is in first or last quartile
    position = case_when(
      trial_number_in_block <= ceiling(total_trials_in_block * 0.25) ~ "first_quart",
      trial_number_in_block > floor(total_trials_in_block * 0.75) ~ "last_quart",
      TRUE ~ "middle"
    )
  ) %>%
  ungroup() %>%
  # Keep only first and last quartile
  filter(position %in% c("first_quart", "last_quart"))

df.ease.part.var <- df.ease.position %>%
  group_by(subject_id, talker, study, block_rel, position) %>%
  summarise(
    mean_response = mean(response_com),
    sd_response = sd(response_com),
    .groups = 'drop'
  ) 

# Step 2: Calculate group-level means and SDs
df.ease.part.sum <- df.ease.part.var %>%
  group_by(talker, study, position) %>%
  summarise(
    mean_of_means = mean(mean_response, na.rm = TRUE),
    mean_of_sds = mean(sd_response, na.rm = TRUE),
    se_of_means = sd(mean_response, na.rm = TRUE) / sqrt(n()),
    se_of_sds = sd(sd_response, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

plot.ease.mean.expl <- ggplot(df.ease.part.sum, 
                 aes(x = talker, y = mean_of_means, fill = position)) +
  geom_col(position = position_dodge(width = 0.8), alpha = 0.7) +
  facet_grid(~study,
             scales = "free_x") +
  labs(x = "Talker", y = "Mean Response", fill = "Quartile") +
  theme_minimal()

plot.ease.sd.expl <- ggplot(df.ease.part.sum, 
               aes(x = talker, y = mean_of_sds, fill = position)) +
  geom_col(position = position_dodge(width = 0.8), alpha = 0.7) +
  facet_grid(~study,
             scales = "free_x") +
  coord_cartesian(ylim = c(0,0.35)) +
  labs(x = "Talker", 
       y = "Variability (SD)", 
       fill = "Quartile", 
       title = "Comfortable/Awkward Trials") 

plot.ease.mean.expl / plot.ease.sd.expl + plot_layout(guides = "collect")
```

```{r}
# Step 1: Calculate within-participant variability
df.sharp.position <- df.sharp %>%
  group_by(subject_id, talker, study, block_rel) %>%
  arrange(trial_in_block_recode) %>%  # Make sure trials are in order
  mutate(
    trial_number_in_block = row_number(),
    total_trials_in_block = n(),
    # Determine if trial is in first or last quartile
    position = case_when(
      trial_number_in_block <= ceiling(total_trials_in_block * 0.25) ~ "first_quart",
      trial_number_in_block > floor(total_trials_in_block * 0.75) ~ "last_quart",
      TRUE ~ "middle"
    )
  ) %>%
  ungroup() %>%
  # Keep only first and last quartile
  filter(position %in% c("first_quart", "last_quart"))

df.sharp.part.var <- df.sharp.position %>%
  group_by(subject_id, talker, study, block_rel, position) %>%
  summarise(
    mean_response = mean(response_sharp),
    sd_response = sd(response_sharp),
    .groups = 'drop'
  ) 

# Step 2: Calculate group-level means and SDs
df.sharp.part.sum <- df.sharp.part.var %>%
  group_by(talker, study, position) %>%
  summarise(
    mean_of_means = mean(mean_response, na.rm = TRUE),
    mean_of_sds = mean(sd_response, na.rm = TRUE),
    se_of_means = sd(mean_response, na.rm = TRUE) / sqrt(n()),
    se_of_sds = sd(sd_response, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

plot.sharp.mean.expl <- ggplot(df.sharp.part.sum, 
                 aes(x = talker, y = mean_of_means, fill = position)) +
  geom_col(position = position_dodge(width = 0.8), alpha = 0.7) +
  facet_grid(~study,
             scales = "free_x") +
  labs(x = "Talker", y = "Mean Response", fill = "Quartile") +
  theme_minimal()

plot.sharp.sd.expl <- ggplot(df.sharp.part.sum, 
               aes(x = talker, y = mean_of_sds, fill = position)) +
  geom_col(position = position_dodge(width = 0.8), alpha = 0.7) +
  facet_grid(~study,
             scales = "free_x") +
  coord_cartesian(ylim = c(0,0.35)) +
  labs(x = "Talker", 
       y = "Response Variability (SD)", 
       fill = "Quartile",
       title = "Sharp/Dull Trials") 

plot.sharp.mean.expl / plot.sharp.sd.expl + plot_layout(guides = "collect")
```

```{r}
# Step 1: Calculate within-participant variability
df.express.position <- df.express %>%
  group_by(subject_id, talker, study, block_rel) %>%
  arrange(trial_in_block_recode) %>%  # Make sure trials are in order
  mutate(
    trial_number_in_block = row_number(),
    total_trials_in_block = n(),
    # Determine if trial is in first or last quartile
    position = case_when(
      trial_number_in_block <= ceiling(total_trials_in_block * 0.25) ~ "first_quart",
      trial_number_in_block > floor(total_trials_in_block * 0.75) ~ "last_quart",
      TRUE ~ "middle"
    )
  ) %>%
  ungroup() %>%
  # Keep only first and last quartile
  filter(position %in% c("first_quart", "last_quart"))

df.express.part.var <- df.express.position %>%
  group_by(subject_id, talker, study, block_rel, position) %>%
  summarise(
    mean_response = mean(response_emo),
    sd_response = sd(response_emo),
    .groups = 'drop'
  ) 

# Step 2: Calculate group-level means and SDs
df.express.part.sum <- df.express.part.var %>%
  group_by(talker, study, position) %>%
  summarise(
    mean_of_means = mean(mean_response, na.rm = TRUE),
    mean_of_sds = mean(sd_response, na.rm = TRUE),
    se_of_means = sd(mean_response, na.rm = TRUE) / sqrt(n()),
    se_of_sds = sd(sd_response, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

plot.express.mean.expl <- ggplot(df.express.part.sum, 
                 aes(x = talker, y = mean_of_means, fill = position)) +
  geom_col(position = position_dodge(width = 0.8), alpha = 0.7) +
  facet_grid(~study,
             scales = "free_x") +
  labs(x = "Talker", y = "Mean Response", fill = "Quartile") 

plot.express.sd.expl <- ggplot(df.express.part.sum, 
               aes(x = talker, y = mean_of_sds, fill = position)) +
  geom_col(position = position_dodge(width = 0.8), alpha = 0.7) +
  facet_grid(~study,
             scales = "free_x") +
  coord_cartesian(ylim = c(0,0.35)) +
  labs(x = "Talker", 
       y = "Response Variability (SD)", 
       fill = "Quartile",
       title = "Emotive/Robotic Trials")

plot.express.mean.expl / plot.express.sd.expl + plot_layout(guides = "collect")
```

```{r}
(plot.gender.sd.expl + plot.ease.sd.expl) /
(plot.sharp.sd.expl + plot.express.sd.expl) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 7),
    axis.title.y = element_text(size = 6),
    axis.text.x  = element_text(size = 7),
    axis.text.y  = element_text(size = 6),
    plot.title   = element_text(size = 9),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    strip.text = element_text(size = 7),
    legend.position = "bottom")

ggsave(file="./analysis/graphs/joint-sd-expl.pdf",width=8,height=5)
ggsave(file="./analysis/graphs/joint-sd-expl.png",width=8,height=5)
```

