---
title: "2A Only"
author: "Grace Brown"
date: "2026-01-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggplot2)
library(ggdist)
library(MuMIn)
library(emmeans)
library(patchwork)

knitr::opts_knit$set(root.dir = "/Users/gracebrown/qp2_2afc")
setwd("/Users/gracebrown/qp2_2afc")

# color-blind-friendly palette
cbPalette <- c("#E69F00", "#CC79A7", "#0072B2", "#D55E00", "#009E73", "#F0E442", "#56B4E9")
theme_set(theme_bw())
```

## Load Data
```{r load data}
## read messy dataset
### duration of clips
df.time <- read_csv("./data/durationlog2a.csv") 
df.time <- df.time %>% mutate(stimulus = paste0("audio/", filename))
### experimental data
df.trials <- read_csv("./data/trials2a.csv") 
df.survey <- read_csv("./data/survey2a.csv")
df.trials <- left_join(x=df.trials,y=df.survey,by="subject_id")
df.trials <- left_join(x=df.trials, y=df.time, by="stimulus")

## Exclusions by Attention Check
df.exclude_attention <- df.trials %>%  
  filter(trial_type == "html-button-response", correct == FALSE) %>%
  distinct(subject_id)

df.trials <- df.trials %>% 
  anti_join(df.exclude_attention, by = "subject_id")

## Exclusions by Trial Completion 
trial_num = 320 # number of listening trials 
df.exclude_trial <- df.trials %>% 
  filter(!is.na(rt), trial_type == "audio-keyboard-response") %>%
  count(subject_id) %>% 
  filter(n / trial_num < 0.85) %>% # subjects with < 85% completion rate excluded
  distinct(subject_id)

df.trials <- df.trials %>% 
  anti_join(df.exclude_trial, by = "subject_id")

## Recode Variables
df.trials$talker <- factor(df.trials$spk, 
                          levels = c(752, 573, 672, 493),
                          labels = c("1F", "2F", "3F", "4F"))
df.trials$prev_talker <- factor(df.trials$prev_spk, 
                          levels = c(752, 573, 672, 493),
                          labels = c("1F", "2F", "3F", "4F"))
df.trials$rt <- as.numeric(df.trials$rt)
df.trials$log_rt <- log(df.trials$rt)
df.trials$log_rt[is.infinite(df.trials$log_rt)] <- NA
df.trials$sentence_id <- as.factor(df.trials$sentence_id)
df.trials$trial_in_block_recode <- ((df.trials$trial_in_block - 1) %% 40) + 1
df.trials$block_index <- ((df.trials$trial_in_block - 1) %/% 40) + 1
```

## Define Response-Specific Datasets
```{r}
df.gender <- df.trials %>%
  filter(label == "masculine" | label == "feminine") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_fem = ifelse(label == "feminine", 1, 0))

df.ease <- df.trials %>%
  filter(label == "comfortable" | label == "awkward") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_com = ifelse(label == "comfortable", 1, 0))

df.sharp <- df.trials %>%
  filter(label == "sharp" | label == "dull") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_sharp = ifelse(label == "sharp", 1, 0))

df.express <- df.trials %>%
  filter(label == "emotive" | label == "robotic") %>% # select responses of interest
  filter(trial_type == "audio-keyboard-response") %>%
  mutate(response_emo = ifelse(label == "emotive", 1, 0))
```

## Visualizations
### feminine / masculine
#### response 
```{r}
plot.gender.resp <- df.gender %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_fem,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Feminine'",
       title = "Mean Feminine/Masculine Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-gender-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-gender-resp.png",width=7,height=4)

print(plot.gender.resp)

## gender best
df.gender.ag <- df.gender %>%
  group_by(subject_id, talker) %>% 
  summarise(proportion = mean(response_fem,
                              na.rm = T),
            .groups = 'drop')

plot.gender.resp.best <- df.gender.ag %>%
  ggplot(mapping = aes(x = talker, 
                       y = proportion,
                       fill = talker,
                       color = talker)) +
  geom_point(
    position = position_jitter(width = 0.125, 
                               height = 0.005,
                               seed = 123),
    alpha = 0.2, 
    size = 2
  ) +
  geom_boxplot(
    width = 0.12,
    outlier.shape = NA,
    position = position_nudge(x = 0.225),
    alpha = 0.5,
    notch = T, 
    color = "black"
  ) +
  stat_summary(
    fun.data = "mean_cl_boot",
    geom = "pointrange",
    color = "black",
    size = 0.4,
    position = position_nudge(x = 0.225)
  ) +
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Feminine'",
       title = "Mean Feminine/Masculine Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-gender-resp-best.pdf",width=5,height=5)
ggsave(file="./analysis/graphs/2a-plot-gender-resp-best.png",width=5,height=5)

print(plot.gender.resp.best)
```

#### response time
```{r}
# central tendencies 
plot.gender.rt.mean <- df.gender %>% 
  ggplot(mapping = aes(x = talker, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Feminine/Masculine Response Times by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-gender-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-gender-rt-mean.png",width=7,height=4)

print(plot.gender.rt.mean)
  
# trend within block 
plot.gender.rt.trend <- df.gender %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  coord_cartesian(ylim = c(1500,2850)) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Feminine/Masculine Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker") 

ggsave(file="./analysis/graphs/2a-plot-gender-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-gender-rt-trend.png",width=7,height=4)

print(plot.gender.rt.trend)

# trend within block + indiv obs
plot.gender.rt.trend.ind <- df.gender %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Feminine/Masculine Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-gender-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-gender-rt-trend-ind.png",width=7,height=4)

print(plot.gender.rt.trend.ind)
```

### comfortable / awkward
#### response 
```{r}
plot.ease.resp <- df.ease %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_com,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Comfortable'",
       title = "Mean Comfortable/Awkward Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-ease-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-ease-resp.png",width=7,height=4)

print(plot.ease.resp)

## comfort best
df.ease.ag <- df.ease %>%
  group_by(subject_id, talker) %>% 
  summarise(proportion = mean(response_com,
                              na.rm = T),
            .groups = 'drop')

plot.ease.resp.best <- df.ease.ag %>%
  ggplot(mapping = aes(x = talker, 
                       y = proportion,
                       fill = talker,
                       color = talker)) +
  geom_point(
    position = position_jitter(width = 0.125, 
                               height = 0.005,
                               seed = 123),
    alpha = 0.2, 
    size = 2
  ) +
  geom_boxplot(
    width = 0.12,
    outlier.shape = NA,
    position = position_nudge(x = 0.225),
    alpha = 0.5,
    notch = T, 
    color = "black"
  ) +
  stat_summary(
    fun.data = "mean_cl_boot",
    geom = "pointrange",
    color = "black",
    size = 0.4,
    position = position_nudge(x = 0.225)
  ) +
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Comfortable'",
       title = "Mean Comfortable/Awkward Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-ease-resp-best.pdf",width=5,height=5)
ggsave(file="./analysis/graphs/2a-plot-ease-resp-best.png",width=5,height=5)

print(plot.ease.resp.best)
```

#### response time
```{r}
# central tendencies 
plot.ease.rt.mean <-df.ease %>% 
  ggplot(mapping = aes(x = talker, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Comfortable/Awkward Response Times by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-ease-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-ease-rt-mean.png",width=7,height=4)

print(plot.ease.rt.mean)
  
# trend within block 
plot.ease.rt.trend <- df.ease %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  coord_cartesian(ylim = c(1600,2800)) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Comfortable/Awkward Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-ease-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-ease-rt-trend.png",width=7,height=4)

print(plot.ease.rt.trend)

# trend within block + indiv obs
plot.ease.rt.trend.ind <- df.ease %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Comfortable/Awkward Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-ease-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-ease-rt-trend-ind.png",width=7,height=4)

print(plot.ease.rt.trend.ind)
```

### sharp / dull
#### response 
```{r}
plot.sharp.resp <- df.sharp %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_sharp,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Sharp'",
       title = "Mean Sharp/Dull Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-sharp-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-sharp-resp.png",width=7,height=4)

print(plot.sharp.resp)

## sharp best
df.sharp.ag <- df.sharp %>%
  group_by(subject_id, talker) %>% 
  summarise(proportion = mean(response_sharp,
                              na.rm = T),
            .groups = 'drop')

plot.sharp.resp.best <- df.sharp.ag %>%
  ggplot(mapping = aes(x = talker, 
                       y = proportion,
                       fill = talker,
                       color = talker)) +
  geom_point(
    position = position_jitter(width = 0.125, 
                               height = 0.005,
                               seed = 123),
    alpha = 0.2, 
    size = 2
  ) +
  geom_boxplot(
    width = 0.12,
    outlier.shape = NA,
    position = position_nudge(x = 0.225),
    alpha = 0.5,
    notch = T, 
    color = "black"
  ) +
  stat_summary(
    fun.data = "mean_cl_boot",
    geom = "pointrange",
    color = "black",
    size = 0.4,
    position = position_nudge(x = 0.225)
  ) +
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Sharp'",
       title = "Mean Sharp/Dull Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-sharp-resp-best.pdf",width=5,height=5)
ggsave(file="./analysis/graphs/2a-plot-sharp-resp-best.png",width=5,height=5)

print(plot.sharp.resp.best)
```

#### response time
```{r}
# central tendencies 
plot.sharp.rt.mean <- df.sharp %>% 
  ggplot(mapping = aes(x = talker, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Sharp/Dull Response Times by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-sharp-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-sharp-rt-mean.png",width=7,height=4)

print(plot.sharp.rt.mean)
  
# trend within block 
plot.sharp.rt.trend <- df.sharp %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  coord_cartesian(ylim = c(1500,2850)) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Sharp/Dull Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-sharp-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-sharp-rt-trend.png",width=7,height=4)

print(plot.sharp.rt.trend)

# trend within block + indiv obs
plot.sharp.rt.trend.ind <- df.sharp %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Sharp/Dull Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-sharp-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-sharp-rt-trend-ind.png",width=7,height=4)

print(plot.sharp.rt.trend.ind)
```

### emotive / robotic
#### response 
```{r}
plot.express.resp <- df.express %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_emo,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Emotive'",
       title = "Mean Emotive/Robotic Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-express-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-express-resp.png",width=7,height=4)

print(plot.express.resp)

## express best
df.express.ag <- df.express %>%
  group_by(subject_id, talker) %>% 
  summarise(proportion = mean(response_emo,
                              na.rm = T),
            .groups = 'drop')

plot.express.resp.best <- df.express.ag %>%
  ggplot(mapping = aes(x = talker, 
                       y = proportion,
                       fill = talker,
                       color = talker)) +
  geom_point(
    position = position_jitter(width = 0.125, 
                               height = 0.005,
                               seed = 123),
    alpha = 0.2, 
    size = 2
  ) +
  geom_boxplot(
    width = 0.12,
    outlier.shape = NA,
    position = position_nudge(x = 0.225),
    alpha = 0.5,
    notch = T, 
    color = "black"
  ) +
  stat_summary(
    fun.data = "mean_cl_boot",
    geom = "pointrange",
    color = "black",
    size = 0.4,
    position = position_nudge(x = 0.225)
  ) +
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Emotive'",
       title = "Mean Emotive/Robotic Responses by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-express-resp-best.pdf",width=5,height=5)
ggsave(file="./analysis/graphs/2a-plot-express-resp-best.png",width=5,height=5)

print(plot.express.resp.best)
```

#### response time
```{r}
# central tendencies 
plot.express.rt.mean <- df.express %>% 
  ggplot(mapping = aes(x = talker, 
                       y = rt,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,3000)) +
  labs(x = "Talker",
       y = "Mean Response Time from Stimulus Onset (ms)",
       title = "Mean Emotive/Robotic Response Times by Talker") + 
  scale_fill_manual(values = cbPalette,
                    name = "Talker") + 
  theme(legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-express-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-express-rt-mean.png",width=7,height=4)

print(plot.express.rt.mean)
  
# trend within block 
plot.express.rt.trend <- df.express %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       color = talker)) + 
  geom_smooth() + 
  coord_cartesian(ylim = c(1500,2850)) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Emotive/Robotic Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-express-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-express-rt-trend.png",width=7,height=4)

print(plot.express.rt.trend)

# trend within block + indiv obs
plot.express.rt.trend.ind <- df.express %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = rt, 
                       group = talker,
                       color = talker)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(se = T) +
  labs(x = "Within-Block Trial #",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Mean Emotive/Robotic Response Times by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-express-rt-trend-ind.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-express-rt-trend-ind.png",width=7,height=4)

print(plot.express.rt.trend.ind)
```

## Visualizations - Grouped 
### response
```{r}
(plot.gender.resp + plot.ease.resp) /
(plot.sharp.resp + plot.express.resp) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 0),
    axis.title.y = element_text(size = 6),
    axis.text.x  = element_text(size = 6),
    axis.text.y  = element_text(size = 5),
    plot.title   = element_text(size = 9),
    legend.position = "bottom")

ggsave(file="./analysis/graphs/2a-plot-all-resp.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-all-resp.png",width=7,height=4)
```

```{r}
(plot.gender.resp.best + plot.ease.resp.best) /
(plot.sharp.resp.best + plot.express.resp.best) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 9),
    axis.title.y = element_text(size = 9),
    axis.text.x  = element_text(size = 7),
    axis.text.y  = element_text(size = 7),
    plot.title   = element_text(size = 0),
    legend.position = "none")

ggsave(file="./analysis/graphs/2a-plot-all-resp-best.pdf",width=6,height=7)
ggsave(file="./analysis/graphs/2a-plot-all-resp-best.png",width=6,height=7)
```


### response time
```{r}
(plot.gender.rt.mean + plot.ease.rt.mean) /
(plot.sharp.rt.mean + plot.express.rt.mean) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 0),
    axis.title.y = element_text(size = 4),
    axis.text.x  = element_text(size = 6),
    axis.text.y  = element_text(size = 5),
    plot.title   = element_text(size = 8),
    legend.position = "bottom")

ggsave(file="./analysis/graphs/2a-plot-all-rt-mean.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-all-rt-mean.png",width=7,height=4)
```

```{r}
(plot.gender.rt.trend + plot.ease.rt.trend) /
(plot.sharp.rt.trend + plot.express.rt.trend) +
  plot_annotation(
    tag_levels = "a",
    tag_prefix = "",
    tag_suffix = "",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 14)
    )
  ) +
  plot_layout(guides = "collect") &
  theme(
    axis.title.x = element_text(size = 6),
    axis.title.y = element_text(size = 4),
    axis.text.x  = element_text(size = 6),
    axis.text.y  = element_text(size = 5),
    plot.title   = element_text(size = 7),
    legend.position = "bottom")

ggsave(file="./analysis/graphs/2a-plot-all-rt-trend.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-all-rt-trend.png",width=7,height=4)
```


## Models
### feminine / masculine
```{r}
fit.gender <- glmer(formula = response_fem ~ 1 + talker + 
                      scale(trial_in_block_recode) +
                      scale(milliseconddur) + 
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = df.gender)

summary(fit.gender)

emmeans(fit.gender, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.gender.logrt <- lmer(formula = log_rt ~ 1 + talker*scale(trial_in_block_recode) + 
                           scale(milliseconddur) + 
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.gender)

summary(fit.gender.logrt)

emmeans(fit.gender.logrt, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.gender.rawrt <- lmer(formula = rt ~ 1 + talker*scale(trial_in_block_recode) + 
                           scale(milliseconddur) + 
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.gender)

summary(fit.gender.rawrt)

emmeans(fit.gender.rawrt, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()
```

### comfortable / awkward
```{r}
fit.ease <- glmer(formula = response_com ~ 1 + talker +
                    scale(trial_in_block_recode) + 
                    scale(milliseconddur) + 
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = df.ease)

summary(fit.ease)

emmeans(fit.ease, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.ease.logrt <- lmer(formula = log_rt ~ 1 + talker*scale(trial_in_block_recode) +
                         scale(milliseconddur) + 
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.ease)

summary(fit.ease.logrt)

emmeans(fit.ease.logrt, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

fit.ease.rawrt <- lmer(formula = rt ~ 1 + talker*scale(trial_in_block_recode) +
                         scale(milliseconddur) + 
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.ease)

summary(fit.ease.rawrt)

emmeans(fit.ease.rawrt, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()
```

### sharp / dull
```{r}
fit.sharp <- glmer(formula = response_sharp ~ 1 + talker +
                       scale(trial_in_block_recode) +
                     scale(milliseconddur) + 
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = df.sharp)

summary(fit.sharp)

emmeans(fit.sharp, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.sharp.logrt <- lmer(formula = log_rt ~ 1 + talker*scale(trial_in_block_recode) +
                          scale(milliseconddur) + 
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.sharp)

summary(fit.sharp.logrt)

emmeans(fit.sharp.logrt, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

fit.sharp.rawrt <- lmer(formula = rt ~ 1 + talker*scale(trial_in_block_recode) +
                          scale(milliseconddur) + 
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.sharp)

summary(fit.sharp.rawrt)

emmeans(fit.sharp.rawrt, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()
```

### emotive / robotic
```{r}
fit.express <- glmer(formula = response_emo ~ 1 + talker +
                       scale(trial_in_block_recode) +
                       scale(milliseconddur) + 
                       (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   family = "binomial",
                   data = df.express)

summary(fit.express)

emmeans(fit.express, 
        specs = pairwise ~ talker) %>% 
  pluck("contrasts") %>%
  summary()

fit.express.logrt <- lmer(formula = log_rt ~ 1 + talker*scale(trial_in_block_recode) +
                            scale(milliseconddur) + 
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.express)

summary(fit.express.logrt)

emmeans(fit.express.logrt, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()

fit.express.rawrt <- lmer(formula = rt ~ 1 + talker*scale(trial_in_block_recode) +
                            scale(milliseconddur) + 
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.express)

summary(fit.express.rawrt)

emmeans(fit.express.rawrt, 
        specs = pairwise ~ talker,
        lmerTest.limit = 11569) %>% 
  pluck("contrasts") %>%
  summary()
```

### response times over all response item pairs
```{r}
fit.all.logrt <- lmer(formula = log_rt ~ 1 + talker*dimension + 
                        scale(trial_in_block_recode) +
                        scale(milliseconddur) + 
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.trials)

summary(fit.all.logrt)

emmeans(fit.all.logrt, 
        specs = pairwise ~ dimension,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.all.logrt, 
        specs = pairwise ~ talker | dimension,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()

fit.all.rawrt <- lmer(formula = rt ~ 1 + talker*dimension + 
                        scale(trial_in_block_recode) +
                        scale(milliseconddur) + 
                         (1 | subject_id) +
                       (1 | sentence_id) +
                       (1 | block_index),
                   data = df.trials)

summary(fit.all.rawrt)

emmeans(fit.all.rawrt, 
        specs = pairwise ~ dimension,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()

emmeans(fit.all.rawrt, 
        specs = pairwise ~ talker | dimension,
        lmerTest.limit = 46919) %>% 
  pluck("contrasts") %>%
  summary()
```

## Exploratory Analysis
### tidying up 
```{r}
prev_talker.labs <- c("Prev: 1F", "Prev: 2F", "Prev: 3F", "Prev: 4F")
names(prev_talker.labs) <- c("1F", "2F", "3F", "4F")
```

### feminine / masculine
#### response by prev_talker
```{r}
plot.gender.resp.expl <- df.gender %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_fem,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Feminine'",
       title = "Mean Feminine/Masculine Responses by Talker") + 
  facet_grid(~prev_talker,
             labeller = labeller(prev_talker = prev_talker.labs)) +
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-gender-resp-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-gender-resp-expl.png",width=7,height=4)

print(plot.gender.resp.expl)
```

#### response by trial
```{r}
# trend within block + indiv obs
plot.gender.trial.expl <- df.gender %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = response_fem, 
                       group = talker,
                       color = talker)) + 
  geom_smooth(se = T) +
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Within-Block Trial #",
       y = "Mean Proportion 'Feminine'",
       title = "Mean Feminine/Masculine Responses by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-gender-trial-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-gender-trial-expl.png",width=7,height=4)

print(plot.gender.trial.expl)
```

#### response time by sentence
```{r}
# trend within block + indiv obs
plot.gender.id.expl <- df.gender %>% 
  ggplot(mapping = aes(x = sentence_id, 
                       y = rt,
                       color = talker)) + 
  stat_summary(fun = "mean",
               geom = "point",
               position = position_dodge(0.9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(0.9)) +
  labs(x = "Talker",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Response Times by Talker and Stimulus Sentence") +
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-gender-id-expl.pdf",width=25,height=4)
ggsave(file="./analysis/graphs/2a-plot-gender-id-expl.png",width=25,height=4)

print(plot.gender.id.expl)
```

### comfortable / awkward
#### response by prev_talker
```{r}
plot.ease.resp.expl <- df.ease %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_com,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Comfortable'",
       title = "Mean Comfortable/Awkward Responses by Talker") + 
  facet_grid(~prev_talker,
             labeller = labeller(prev_talker = prev_talker.labs)) +
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-ease-resp-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-ease-resp-expl.png",width=7,height=4)

print(plot.ease.resp.expl)
```

#### response by trial
```{r}
# trend within block + indiv obs
plot.ease.trial.expl <- df.ease %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = response_com, 
                       group = talker,
                       color = talker)) + 
  geom_smooth(se = T) +
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Within-Block Trial #",
       y = "Mean Proportion 'Comfortable'",
       title = "Mean Comfortable/Awkward Responses by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-ease-trial-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-ease-trial-expl.png",width=7,height=4)

print(plot.ease.trial.expl)
```

#### response time by sentence
```{r}
# trend within block + indiv obs
plot.ease.id.expl <- df.ease %>% 
  ggplot(mapping = aes(x = sentence_id, 
                       y = rt,
                       color = talker)) + 
  stat_summary(fun = "mean",
               geom = "point",
               position = position_dodge(0.9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(0.9)) +
  labs(x = "Talker",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Response Times by Talker and Stimulus Sentence") +
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-ease-id-expl.pdf",width=25,height=4)
ggsave(file="./analysis/graphs/2a-plot-ease-id-expl.png",width=25,height=4)

print(plot.ease.id.expl)
```

### sharp / dull
#### response by prev_talker
```{r}
plot.sharp.resp.expl <- df.sharp %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_sharp,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Sharp'",
       title = "Mean Sharp/Dull Responses by Talker") + 
  facet_grid(~prev_talker,
             labeller = labeller(prev_talker = prev_talker.labs)) +
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-sharp-resp-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-sharp-resp-expl.png",width=7,height=4)

print(plot.sharp.resp.expl)
```

#### response by trial
```{r}
# trend within block + indiv obs
plot.sharp.trial.expl <- df.sharp %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = response_sharp, 
                       group = talker,
                       color = talker)) + 
  geom_smooth(se = T) +
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Within-Block Trial #",
       y = "Mean Proportion 'Sharp'",
       title = "Mean Sharp/Dull Responses by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-sharp-trial-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-sharp-trial-expl.png",width=7,height=4)

print(plot.sharp.trial.expl)
```

#### response time by sentence
```{r}
# trend within block + indiv obs
plot.sharp.id.expl <- df.sharp %>% 
  ggplot(mapping = aes(x = sentence_id, 
                       y = rt,
                       color = talker)) + 
  stat_summary(fun = "mean",
               geom = "point",
               position = position_dodge(0.9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(0.9)) +
  labs(x = "Talker",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Response Times by Talker and Stimulus Sentence") +
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-sharp-id-expl.pdf",width=25,height=4)
ggsave(file="./analysis/graphs/2a-plot-sharp-id-expl.png",width=25,height=4)

print(plot.sharp.id.expl)
```

### emotive / robotic
#### response by prev_talker
```{r}
plot.express.resp.expl <- df.express %>%
  ggplot(mapping = aes(x = talker, 
                       y = response_emo,
                       fill = talker)) +
  stat_summary(fun = "mean",
               geom = "bar") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Talker",
       y = "Mean Proportion 'Emotive'",
       title = "Mean Emotive/Robotic Responses by Talker") + 
  facet_grid(~prev_talker,
             labeller = labeller(prev_talker = prev_talker.labs)) +
  scale_fill_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-express-resp-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-express-resp-expl.png",width=7,height=4)

print(plot.express.resp.expl)
```

#### response by trial
```{r}
# trend within block + indiv obs
plot.express.trial.expl <- df.express %>% 
  ggplot(mapping = aes(x = trial_in_block_recode, 
                       y = response_emo, 
                       group = talker,
                       color = talker)) + 
  geom_smooth(se = T) +
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Within-Block Trial #",
       y = "Mean Proportion 'Emotive'",
       title = "Mean Emotive/Robotic Responses by Talker and Trial") + 
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-express-trial-expl.pdf",width=7,height=4)
ggsave(file="./analysis/graphs/2a-plot-express-trial-expl.png",width=7,height=4)

print(plot.express.trial.expl)
```

#### response time by sentence
```{r}
# trend within block + indiv obs
plot.express.id.expl <- df.express %>% 
  ggplot(mapping = aes(x = sentence_id, 
                       y = rt,
                       color = talker)) + 
  stat_summary(fun = "mean",
               geom = "point",
               position = position_dodge(0.9)) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               position = position_dodge(0.9)) +
  labs(x = "Talker",
       y = "Response Time from Stimulus Onset (ms)",
       title = "Response Times by Talker and Stimulus Sentence") +
  scale_color_manual(values = cbPalette,
                    name = "Talker")

ggsave(file="./analysis/graphs/2a-plot-express-id-expl.pdf",width=25,height=4)
ggsave(file="./analysis/graphs/2a-plot-express-id-expl.png",width=25,height=4)

print(plot.express.id.expl)
```
